---
title: "Programs: Replication and Reproducibility in Social Sciences and Statistics: Context, Concerns, and Concrete Measures"
author: "Lars Vilhuber"
date: "`r Sys.Date()`"
output: 
  html_document: 
    keep_md: yes
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Program directory
This directory contains all programs necessary to run the download and analysis. They can be run separately, or from the master document (this README). 

## Setup
Most parameters are set in the `config.R`:
```{r setup_config}
source(file.path(rprojroot::find_rstudio_root_file(),"pathconfig.R"),echo=TRUE)
source(file.path(programs,"config.R"), echo=TRUE)
```

Any libraries needed are called and if necessary installed through `libraries.R`:

```{r setup_libraries}
source(file.path(basepath,"global-libraries.R"),echo=TRUE)
source(file.path(programs,"libraries.R"), echo=TRUE)
```



## Download the survey data from Google Sheet
The responses to the surveys are stored on Google Sheets. 
```{r download_replication,eval=FALSE,cache=TRUE}
source(file.path(programs,"01_download_surveys.R"),echo=TRUE)
```

## Combine various sites into one file
We combine the various files - it evolves a bit over time, so we need to possibly do some consolidation.

TBD


## Core analysis and figures
We can now tabulate the results from the survey

TBD
