---
title: "Programs: Replication and Reproducibility in Social Sciences and Statistics: Context, Concerns, and Concrete Measures"
author: "Lars Vilhuber"
date: "`r Sys.Date()`"
output: 
  html_document: 
    keep_md: yes
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Program directory
This directory contains all programs necessary to run the download and analysis. They can be run separately, or from the master document (this README). 

## Setup
Most parameters are set in the `config.R`:
```{r setup_config, 	message = FALSE,	warning = FALSE,	include=TRUE}
source(file.path(rprojroot::find_rstudio_root_file(),"pathconfig.R"),echo=FALSE)
source(file.path(programs,"config.R"), echo=FALSE)
```

Any libraries needed are called and if necessary installed through `libraries.R`:

```{r setup_libraries}
knitr::opts_chunk$set(warning = FALSE, message = TRUE, include = FALSE)
source(file.path(basepath,"global-libraries.R"),echo=FALSE)
source(file.path(programs,"libraries.R"), echo=FALSE)
```



## Download the survey data from Google Sheet
The responses to the surveys are stored on Google Sheets. Programs make no attempt to verify if the data previously downloaded (in [../data/survey_data](../data/survey_data)) are older than the data on the web. In order to update the data, delete the relevant file, and run the programs again. The following program is NOT automatically run when executing this README - change the `eval=FALSE` to `eval=TRUE` to run it, or run it manually.

```{r download_survey,eval=FALSE,include=TRUE,cache=TRUE}
source(file.path(programs,"01_download_surveys.R"),echo=TRUE)
```

## Combine various sites into one file
We combine the various files - it evolves a bit over time, so we need to possibly do some consolidation.

```{r combine_survey,eval=TRUE,include=TRUE,cache=TRUE}
source(file.path(programs,"02_combine_surveys.R"),echo=TRUE)
```



## Core analysis and figures
We can now tabulate the results from the survey.

TBD.


